Open Policing Project - City: Coverage Rates

### 2018-10-26 lib/bunching_report.Rmd
progress

```{r ok, fig.height=3.75, fig.width=7}
ok <- opp_load_data("ok", "oklahoma city")
ok <-
  ok %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
ok_bt <- bunching_test(ok, division, hour_of_day, age_group, vehicle_make)
ok_bt$results$plots$over
ok_bt$results$plots$coefficient
ok_bt$results$plots$bunching
ok_bt$results$plots$lenience
```

@@

```{r dallas_over, fig.height=3.75, fig.width=7}
da <- opp_load_data("tx", "dallas")
dar <- prepare(da)
das <- prepare(da, subject_sex, "male")
plot_over(dar, "Dallas MPH Over by Race")
plot_over(das, "Dallas MPH Over by Sex", is_male)
```

```{r dallas_bunching, fig.height=4, fig.width=7}
plot_bunching(dar, "Dallas Bunching by Race")
plot_bunching(das, "Dallas Bunching by Sex")
```

Officer is considered lenient if $\le 3\%$ of stops at bunch points

```{r dallas_lenience, fig.height=4, fig.width=7}
plot_lenient(dar, "Dallas Over by Lenience and Race")
plot_lenient(das, "Dallas Over by Lenience and Sex", is_male)
```

@@

```{r plano_over, fig.height=3.75, fig.width=7}
pl <- opp_load_data("tx", "plano")
plr <- prepare(pl)
pls <- prepare(pl, subject_sex, "male")
plot_over(plr, "Plano MPH Over by Race")
plot_over(pls, "Plano MPH Over by Sex", is_male)
```

```{r plano_bunching, fig.height=4, fig.width=7}
plot_bunching(plr, "Plano Bunching by Race")
plot_bunching(pls, "Plano Bunching by Sex")
```

Officer is considered lenient if $\le 3\%$ of stops at bunch points

```{r plano_lenience, fig.height=4, fig.width=7}
plot_lenient(plr, "Plano Over by Lenience and Race")
plot_lenient(pls, "Plano Over by Lenience and Sex", is_male)
```

>>>>

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(tbl, division, hour_of_day, age_group, vehicle_make)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(tbl, region, hour_of_day, vehicle_type)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```
\newpage

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(tbl, hour_of_day, vehicle_make)
bt$results$plots$over
bt$results$plots$coefficient
bt$results$plots$bunching
bt$results$plots$lenience
```
